GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring

### 2020-12-20 paper/manuscript-iot.tex
sub 2 iot version

	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007.}% <-this % stops a space
	}

>>>>

	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
		\thanks{This research was funded by the National Key R&D Program of China (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007.}% <-this % stops a space
	}
